---
title: "Examples"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Motor Trend Car Test Research
==================================================
This data represents some of the teams findings in our motor trend car testing project.

##  {.tabset}

### Scatter Plot


```{r, include = FALSE}
library(plotly)

data<-mtcars

data$cyl = as.factor(data$cyl)

legendtitle = list(yref='paper',xref="paper",y=1.05,x=1.1, text="Cylinder",showarrow=F)
legendtitle2 = list(yref='paper',xref="paper",y=1.05,x=1.1, text="Gear",showarrow=F)
  g3 <-filter(data, gear == 3)
    g4 <-filter(data, gear ==4)
      g5 <-filter(data, gear == 5)
      gears <- data.frame(cyl = c(g3$cyl, g4$cyl, g5$cyl),
                          hp = c(g3$hp, g4$hp, g5$hp),
                          gear = c(g3$gear, g4$gear, g5$gear)
                          )

```

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.width="100%" }


   plot_ly(data, x=~hp, y=~wt, color  = ~cyl, type = "scatter", text = ~paste("Gears:", gear, '<br>disp:', disp))%>%
  layout(
    title = 'Horsepower vs. Weight',  annotations=legendtitle,  xaxis = list(title = 'Horsepower'), 
         yaxis = list(title = 'Weight'))
 
```


### Bar Plot


```{r, echo = FALSE, message=FALSE, warning=FALSE, out.width="100%" }



 plot_ly(gears, x=~cyl, y=~hp, type = "bar",name = ~gear)%>%
  layout(
    title = 'Cylinder vs. Horsepower at Varied Gears', annotations = legendtitle2, xaxis = list(title = 'Cylinder'), 
         yaxis = list(title = 'Horsepower'))



```



### Heat Map
```{r, echo = FALSE, message=FALSE, warning=FALSE, out.width="100%" }

plot_ly(data,
            x = ~wt, 
            y = ~disp, 
            z = ~mpg, 
           
            colorscale = list(c(0,'red'),
                              c(0.33,'orange'),
                              c(0.66, 'yellow'),
                              c(1, 'green')),
            colorbar=list(
              title="MPG"
            ), 
                              type = "contour")%>%
      layout(title = 'MPG vs. Displacement & Weight',  xaxis = list(title = 'Weight'), 
             yaxis = list(title = 'Displacement'))


```
  
### Test  
  
```{r, echo = FALSE, message=FALSE, warning=FALSE, out.width="100%" }
  dat <- mtcars
dat$cyl <- factor(dat$cyl)
dat$car <- rownames(mtcars)

dat %>% 
  tidyr::pivot_longer(c(mpg, hp, qsec)) %>% 
  plot_ly(x = ~car, y = ~value, color = ~cyl, symbol = ~name) %>%
  add_trace(type='scatter', mode='markers', name = ~cyl) %>% 
  layout(
    updatemenus = list(
      list(
        type = "list",
        label = 'Category',
        buttons = list(
          list(method = "restyle",
               args = list('visible', c(TRUE, FALSE, FALSE)),
               label = "hp"),
          list(method = "restyle",
               args = list('visible', c(FALSE, TRUE, FALSE)),
               label = "mpg"),
          list(method = "restyle",
               args = list('visible', c(FALSE, FALSE, TRUE)),
               label = "qsec")
        )
      )
    )
  )
```
  
  
  
  

Iris Flower Research
====================================================
This data represents some of the teams findings in our iris flower research.

##  {.tabset}

### Customize

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.width="100%" }



   
   p <- plot_ly(iris, x = ~Sepal.Length, y = ~Sepal.Width, color = ~Species, type = "scatter", mode = "markers") %>% 
  layout(title = '',  xaxis = list(title = 'Size (in)', zeroline = FALSE), 
             yaxis = list(title = 'Size (in)', zeroline = FALSE),
    annotations = list(
      list(
        text = "<b>Y:</b>", x=0.1, y=1.05, xref='paper', yref='paper',xanchor = "left", showarrow=FALSE
      ),
      list(
        text = "<b>X:</b>", x=0.6, y=1.05, xref='paper', yref='paper',xanchor = "left", showarrow=FALSE
      )
    ),
    updatemenus = list(
      ## X Axis ##
      list(
        y = 1.06, x = 0.9,
        buttons = list(
          list(method = "restyle",
               args = list("x", list(iris$Sepal.Width)),  # put it in a list
               label = "Sepal Width"),
          list(method = "restyle",
               args = list("x", list(iris$Sepal.Length)),  # put it in a list
               label = "Sepal Length"),
       list(method = "restyle",
               args = list("x", list(iris$Petal.Length)),  # put it in a list
               label = "Petal Length"),
       list(method = "restyle",
               args = list("x", list(iris$Petal.Width)),  # put it in a list
               label = "Petal Width"))),
      
      ## Y Axis ##
      list(
        y = 1.06,x= 0.4,
        buttons = list(
           list(method = "restyle",
               args = list("y", list(iris$Sepal.Width)),  # put it in a list
               label = "Sepal Width"),
          list(method = "restyle",
               args = list("y", list(iris$Sepal.Length)),  # put it in a list
               label = "Sepal Length"),
       list(method = "restyle",
               args = list("y", list(iris$Petal.Length)),  # put it in a list
               label = "Petal Length"),
       list(method = "restyle",
               args = list("y", list(iris$Petal.Width)),  # put it in a list
               label = "Petal Width")))
    )
    
    
    
    )

p



```

### Boxplots

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.width="100%" }


p <- plot_ly(data = iris, x= ~Species, y = ~Sepal.Width, type = 'box') %>%
 layout(
    annotations = list(
      list(
        text = "<b>Variable:</b>", x=0.05, y=1.13, xref='paper', yref='paper',xanchor = "left", showarrow=FALSE
      )
    ),
    updatemenus = list(
      list(
        type = "list",
        x = 0.25,
        xanchor = "left",
        y = 1.15,
        buttons = list(
          list(
            method = "update",
            args = list(list(y = list(iris$Sepal.Length)),
                        list(yaxis = list(title = "Sepal.Length"))),
            label = "Sepal.Length"
          ),
          list(
            method = "update",
            args = list(list(y =list(iris$Sepal.Width)),
                        list(yaxis = list(title = "Sepal.Width"))),
            label = "Sepal.Width"
          ),
          list(
            method = "update",
            args = list(list(y = list(iris$Petal.Length)),
                        list(yaxis = list(title = "Petal.Length"))),
            label = "Petal.Length"
          ),
          list(
            method = "update",
            args = list(list(y = list(iris$Petal.Width)),
                        list(yaxis = list(title = "Petal.Width"))),
            label = "Petal.Width"
          )
        )
      )
    )
  )
p

```


US Crime Rate Research
======================================================================
This data represents some of the teams findings in our US crime rate research.

##  {.tabset}

### Map


```{r, echo = FALSE, fig.dim=c(10, 6), out.width="100%" }
  library(plotly)
  df <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/2011_us_ag_exports.csv")
  code = df$code
  
    d <- USArrests
  state <- rownames(d)
  rownames(d) <- NULL
  df<- cbind(state,d)

  df <- cbind(df,code)
  
  
  df$hover <- with(df, paste(state, '<br>', "Murders", Murder,'<br>', "Assault", Assault, "<br>",
                             "% Urban Pop.", UrbanPop))
  # give state boundaries a white border
  l <- list(color = toRGB("white"), width = 2)
  # specify some map projection/options
  g <- list(
    scope = 'usa',
    projection = list(type = 'albers usa'),
    showlakes = TRUE,
    lakecolor = toRGB('white')
  )
  
  fig <- plot_geo(df, locationmode = 'USA-states')
  fig <- fig %>% add_trace(
    z = ~Murder, text = ~hover, locations = ~code,
    color = ~Murder, colors = 'Reds'
  )
  fig <- fig %>% colorbar(title = "Murders per 100K")
  fig <- fig %>% layout(
    title = 'US Muder Rates per State<br>(Hover for breakdown)',
    geo = g
  )
  
  fig
```

### Scatter Plot

```{r, echo = FALSE, warning = FALSE, message= FALSE, out.width="100%" }


 plot_ly(
  df, x = ~Murder, y = ~Assault,
  # Hover text:
  text = ~paste(code, '<br> % Urban Pop.:', UrbanPop),
  color = ~UrbanPop, size = ~UrbanPop, type = "scatter"
)%>%
      layout(title = '',  xaxis = list(title = 'Murders/100K', zeroline = FALSE), 
             yaxis = list(title = 'Assaults/100k', zeroline = FALSE))




```


### Bar Plot

```{r, echo = FALSE, message=FALSE, warning=FALSE, out.width="100%" }


df1<- data.frame(
  code = df$code,
  height = df$Assault
)


df2<- data.frame(
  code = df$code,
  height = df$Murder
)

```

```{r, echo = FALSE, warning = FALSE, message= FALSE, out.width="100%" }

p <- plot_ly() %>%
  add_trace(type = 'bar', x=~code,
            y = df2$height, visible=T)  %>%
  add_trace(type = 'bar',x= ~code,
            y = df1$height, visible=F) %>%
  layout(showlegend = FALSE,
         xaxis = list(title = 'Sate'),
    updatemenus = list(
      list(
        yanchor = 'auto',
        buttons = list(
          list(method = "restyle",
               args = list("visible", list(T, F)),
               label = 'Murder'),
          
          list(method = "restyle",
               args = list("visible", list(F,T)),
               label = 'Assault')
        ))))
p

          

```
